Solving TSP With Genetic Algorithms

### 2018-04-12 tex/paper.tex
Fix file path
Add SA algorithm subsection

\documentclass[twocolumn]{article}
\usepackage{graphicx}
\begin{document}	
	\twocolumn[
	\begin{@twocolumnfalse}
		\author{Mohamed Moanis Ali, Michael Sedrak \\  mohamed.moanis.ali@gmail.com, m.sedrak@live.com}
		\title{Solving TSP With Genetic Algorithms}
		\maketitle
		\begin{abstract}
			Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse condimentum, urna nec luctus tincidunt, nisi augue vehicula nulla, sit amet sollicitudin nisi nibh eget diam. Vivamus maximus tortor dolor, non porttitor urna vestibulum eu. Nullam maximus in massa eu lacinia. Curabitur ac risus ac elit euismod placerat quis eu odio. Sed ante ex, congue sit amet enim et, aliquam egestas turpis. Cras purus ex, viverra sit amet augue id, tempus ultricies risus. Aenean eget vestibulum orci. Ut enim nisi, tempor id urna et, dignissim ornare lectus. Nunc lobortis risus neque, a fermentum ante consequat ac. Fusce mollis pretium pellentesque. Vestibulum fermentum ornare elementum. Nam rutrum sem ut est mollis consequat. Morbi at faucibus mi. In ultricies justo non lorem varius, non tristique ante suscipit. Curabitur eget diam tincidunt, venenatis enim sagittis, malesuada magna. Nullam in urna a odio finibus tristique.
		\end{abstract}
	\end{@twocolumnfalse}
	]

@@

	\section{Dataset}
	Datasets for TSP problem contain a wide variety of formats. Cities across a country, VLSI nodes or traveling across the Mona Lisa drawing. But they are all similar in the aspect of the data structure. The structure is a 2-D coordinate point system with euclidean distances as the distance between nodes.
	For our work we selected the Uruguay dataset from the national dataset collection. Uruguay dataset is characterized by 
	\begin{itemize}
		\item 734 unique points (no duplicates)
		\item Optimal tour of length 79114
	\end{itemize}
	\begin{figure}[h!]
		\centering
		\includegraphics[scale=0.3]{./tex/uypoints.jpg}
		\caption{XY coordinate representation of Uruguay dataset}
		\label{fig:uruguay}
	\end{figure}
	A graphical representation of the coordinates of the dataset is shown in figure \ref{fig:uruguay}

@@

	Genetic algorithm is a randomized metaheuristic search technique that simulates the process of evolution and natural selection in order to solve combinatorial optimization problems. Operations like mutation, crossover and selection are used to search for the optimal solution for a given problem.

@@

	\subsection{Simulated Annealing}

	\section{Results}

>>>>

\documentclass[twocolumn]{article}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\begin{document}	
	\twocolumn[
	\begin{@twocolumnfalse}
		\author{Mohamed Moanis Ali, Michael Sedrak \\  mohamed.moanis.ali@gmail.com, m.sedrak@live.com}
		\title{Solving TSP With Genetic Algorithms}
		\maketitle
		\begin{abstract}
			Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse condimentum, urna nec luctus tincidunt, nisi augue vehicula nulla, sit amet sollicitudin nisi nibh eget diam. Vivamus maximus tortor dolor, non porttitor urna vestibulum eu. Nullam maximus in massa eu lacinia. Curabitur ac risus ac elit euismod placerat quis eu odio. Sed ante ex, congue sit amet enim et, aliquam egestas turpis. Cras purus ex, viverra sit amet augue id, tempus ultricies risus. Aenean eget vestibulum orci. Ut enim nisi, tempor id urna et, dignissim ornare lectus. Nunc lobortis risus neque, a fermentum ante consequat ac. Fusce mollis pretium pellentesque. Vestibulum fermentum ornare elementum. Nam rutrum sem ut est mollis consequat. Morbi at faucibus mi. In ultricies justo non lorem varius, non tristique ante suscipit. Curabitur eget diam tincidunt, venenatis enim sagittis, malesuada magna. Nullam in urna a odio finibus tristique.
		\end{abstract}
	\end{@twocolumnfalse}
	]

@@

	Duis porttitor risus id enim fermentum, sed facilisis lacus placerat. Pellentesque ultricies felis vel enim imperdiet, vel dictum lectus porttitor. Etiam maximus dignissim est, non pretium nunc suscipit quis. Aliquam posuere et leo sit amet porttitor. Mauris rhoncus tellus vitae lorem venenatis efficitur. Quisque ut pretium velit. Vivamus luctus dapibus tincidunt. Aenean volutpat semper purus, sed vestibulum leo imperdiet ac. Sed turpis ex, volutpat sit amet ipsum quis, dapibus volutpat ante.
	\section{Dataset}
	Datasets for TSP problem contain a wide variety of formats. Cities across a country, VLSI nodes or traveling across the Mona Lisa drawing. But they are all similar in the aspect of the data structure. The structure is a 2-D coordinate point system with euclidean distances as the distance between nodes.
	For our work we selected the Uruguay dataset from the national dataset collection. Uruguay dataset is characterized by 
	\begin{itemize}
		\item 734 unique points (no duplicates)
		\item Optimal tour of length 79114
	\end{itemize}
	\begin{figure}[h!]
		\centering
		\includegraphics[scale=0.3]{./uypoints.jpg}
		\caption{XY coordinate representation of Uruguay dataset}
		\label{fig:uruguay}
	\end{figure}
	A graphical representation of the coordinates of the dataset is shown in figure \ref{fig:uruguay}

@@

	Genetic algorithm (GA) is a randomized metaheuristic search technique that simulates the process of evolution and natural selection in order to solve combinatorial optimization problems. Operations like mutation, crossover and selection are used to search for the optimal solution for a given problem.

@@

	\subsection{Simulated Annealing}
	 Simulated annealing (SA) is another algorithm that mimic a natural phenomena; this time it is the heat treatment process used on metals. During the annealing process, a metal is heated enough to allow its molecular structure to be altered. The temperature {\bfseries T} is steadily lowered by a cooling constant {$\boldsymbol \beta$}, which subsequently lowers the energy of the atoms and restricts their arrangement until the metal's structure finally becomes set. That in turn, minimizes the number of defects in the structure of the metal.

	 SA can be considered as a modification for greedy search as an attempt to reach an optimal solution rather than getting stuck at a local optimum. For example, consider a problem of searching a function with the goal of reaching the global optimum. A greedy approach would move in the direction that result in a higher gain and stops once no more moves would lead to a higher gain, thus, a greedy approach can miss the global optimal solution.

	 In contrast to greedy approach, SA occasionally allows moves in directions with lower gain that would not have been accessible otherwise. SA starts at random solution -a state {\bfseries S}- and then at each iteration step, the solution is slightly modified in order to choose another search point and move to a new state $\boldsymbol{S\prime}$. This modification is made with a random reorder of a constant number of elements in the solution space {\bfseries M}. The selection process of the new state -solution- considers the change in cost {\bfseries C} - know as {$\boldsymbol \gamma$}- that will be incurred if the new state is chosen. When the cost is going to be lower, the new state is chosen. Else, however, the incurred cost might increase there is still a chance to accept this state with a probability \\{\bfseries P({$\boldsymbol \gamma$}, T)} that is relative to the current temperature of the simulation; that's it, when the current temperature is high, the probability to take worse solutions will be higher as there still more simulation time available to try different search point in order to reach the global optimum.

	 In the context of TSP, each state in SA algorithm is a route between the towns and cities. The cost measured for each route is the distance  between its points and accordingly the optimal solution is that with the minimum distance. SA algorithm would then work in the following steps:
	 \begin{enumerate}
	 	\item Choose random state {\bfseries S} and the starting temperature {\bfseries T} and cooling constant {$\boldsymbol \beta$}.
	 	\item Create new state $\boldsymbol{S\prime}$ by randomly swapping {\bfseries M} cities in the current state.
	 	\item Compute the change in cost \[
	 	\boldsymbol{\gamma = \dfrac{C(S')-C(S)}{C(S)}}
	 	\]
	 	\item If {$\boldsymbol{\gamma \leqslant 0}$, then {\bfseries S =} $\boldsymbol{S\prime}$.}
	 	\item Else, compute the probability \[
	 	\boldsymbol{P(\gamma, T)=}
	 	\begin{cases}
	 	\boldsymbol{1},& \text{if } \boldsymbol{\gamma\leqslant 0}\\
	 	\boldsymbol{e^{\frac{-\gamma}{T}}},& \text{otherwise}
	 	\end{cases} 
	 	\]
	 	\item Randomly assign {\bfseries S =} $\boldsymbol{S\prime}$ using {$\boldsymbol \gamma$}.
	 	\item Repeat steps 2 to 6 until stopping conditions are met; ie, temperature reaches a certain threshold or a required number of iterations is met.
	 \end{enumerate}
	 Finally, the performance of SA can be controlled by the choice of the initial temperature, cooling constant and the number of cities modified in each step. Additionally, the stopping conditions are of quite importance for SA to reach a near optimal solution. If the algorithm is stopped too soon, the approximation will not be as close to the global optimum. And if the algorithm is not stopped soon enough, more time will be wasted on calculations and search steps with little to no gain.
	\section{Results}
